A seamless, client-centric programming model for type safe web applications

### 2014-05-08 paper.tex
Improve description of liftServerIO.
Even better liftServerIO!!11~1

In contrast to \lstinline!liftIO!, the result value of \lstinline!liftServerIO!
is contained within the \lstinline!Server! monad, completely out of reach of the
client. Any client side code is thus free to completely ignore executing
computations lifted using \lstinline!liftServerIO!; since the result of a
server lifted computation is never observable on the client, the client has no
obligation to even produce such a value. Figure \ref{lst:good-state} shows how
to make proper use of server side state.

>>>>

\lstinline!liftServerIO! performs its argument computation once on the server,
in the \lstinline!App! monad, and then returns the result of said computation
inside the \lstinline!Server! monad so that it is only reachable by server side
code.
Any client side code is thus free to completely ignore executing
computations lifted using \lstinline!liftServerIO!; since the result of a
server lifted computation is never observable on the client, the client has no
obligation to even produce such a value. Figure \ref{lst:good-state} shows how
to make proper use of server side state.
